\documentclass[12pt]{article}
\usepackage{a4wide}
\usepackage{latexsym}

\begin{document}
\thispagestyle{empty}

\begin{center}
{\large Database Systems Lab} \\
{\bf Assignment 6: Relation Manager and External Sort Implementation in MuBase} \\
\end{center}

\noindent
Marks: 100 \\

As part of this course, students of your senior batch developed the
foundation layers of {\em MuBase}, a small database management system
modeled after University of Wisconsin's MiniBase.  They implemented
storage manager to keep track of free/allocated disk blocks, 
buffer manager and a B+ tree indexing layer. In this assignment you
will be extending the functionality of {\em MuBase} to provide 
support for relations. At the end of this assignment, {\em MuBase} 
should be able to support the following operations:

\begin{enumerate}
\item Creation of a relation with specified schema
\item Adding/deleting records from a relation
\item Full scan of a relation
\item Predicated scan (search) over a relation (should make
      use of index when available)
\item Sorting of a relation on a specified attribute
\end{enumerate}

The attached tar.gz has 3 sub-directories. The subdir {\em interface}
contains the interfaces of the various layers (already present in 
MuBase, as well as the ones you will be implementing). You will be 
providing the implementation for the classes in {\tt rm.h} and {
\tt sort.h}. The subdir {\em slotted$\_$page} contains interfaces
for the slotted page classes. The subdir {\em mubase} contains
the implementation of storage manager, buffer manager and B+ tree
indexing layer. There may be some minor variations between this
implementation (done by Varun and his team) and the interfaces 
provided in the {\em interface} subdir. 
Go through the README file, it contains important instructions.

Records in a relation will be stored in blocks using the slotted
page organization.  A framework for implementing the get, store 
and delete methods for a slotted page is also provided.

For sorting a relation you will be implementing the external 
sort algorithm (to be discussed in the class).

The project can be done in groups of at most 4 members. Please 
communicate your team composition by sending a mail to the TAs,
with the subject line ``Team for MuBase''. Although this assignment 
can be done in groups, evaluation will be done based on the 
contribution of individuals. So split up the work equally and 
work independently on your chosen module. 
\end{document}

